\newpage

\begin{thebibliography}{20}
\setlength{\itemsep}{-1mm}

\bibitem{ref01}
Zhang, L., Wang, H., \& Chen, M. (2018). Water demand forecasting using grey prediction models: A case study of China. \textit{Water Resources Management}, 32(4), 1347-1362.

\bibitem{ref02}
Wang, J., \& Chen, Y. (2020). Driving factors of water consumption in China: A decomposition analysis. \textit{Journal of Cleaner Production}, 265, 121745.

\bibitem{ref03}
Liu, X., Zhang, Q., \& Li, H. (2022). Agricultural water pricing policy design: A multi-objective optimization approach. \textit{Agricultural Water Management}, 271, 107801.

\bibitem{ref04}
Ministry of Water Resources of China. (2017). \textit{China Water Resources Bulletin 2016}. China Water \& Power Press.

\bibitem{ref05}
National Bureau of Statistics of China. (2017). \textit{China Statistical Yearbook 2017}. China Statistics Press.

\bibitem{ref06}
OECD. (2018). \textit{OECD Environmental Outlook to 2050: The Consequences of Inaction}. OECD Publishing.

\bibitem{ref07}
Deng, J. (1989). Introduction to grey system theory. \textit{The Journal of Grey System}, 1(1), 1-24.

\bibitem{ref08}
Box, G. E., Jenkins, G. M., \& Reinsel, G. C. (2015). \textit{Time Series Analysis: Forecasting and Control}. John Wiley \& Sons.

\bibitem{ref09}
Breiman, L. (2001). Random forests. \textit{Machine Learning}, 45(1), 5-32.

\bibitem{ref10}
Miettinen, K. (2012). \textit{Nonlinear Multiobjective Optimization}. Springer Science \& Business Media.

\bibitem{ref11}
Dalhuisen, J. M., Florax, R. J., De Groot, H. L., \& Nijkamp, P. (2003). Price and income elasticities of residential water demand: A meta-analysis. \textit{Land Economics}, 79(2), 292-308.

\bibitem{ref12}
Worthington, A. C., \& Hoffman, M. (2008). An empirical survey of residential water demand modelling. \textit{Journal of Economic Surveys}, 22(5), 842-871.

\bibitem{ref13}
Scheierling, S. M., Loomis, J. B., \& Young, R. A. (2006). Irrigation water demand: A meta-analysis of price elasticities. \textit{Water Resources Research}, 42(1), W01411.

\bibitem{ref14}
Deb, K., Pratap, A., Agarwal, S., \& Meyarivan, T. (2002). A fast and elitist multiobjective genetic algorithm: NSGA-II. \textit{IEEE Transactions on Evolutionary Computation}, 6(2), 182-197.

\bibitem{ref15}
World Bank. (2019). \textit{High and Dry: Climate Change, Water, and the Economy}. World Bank Publications.

\end{thebibliography}